Manuscript Figures for Genome Biology

### 2018-08-06 manuscript_figures/manuscript_figures.Rmd
Remove Fig 3; adjust legend pos. in inf. cov. plot; fix typo in xlab of rankings boxplot

This is a side-by-side figure displaying the TPR by alpha cutoff, faceted by 
whether the method uses multiple pieces of information or just one (the p-value).
This figure uses the same data as Figure 1.

```{r, Figure3, fig.width = 8, fig.height = 4}
# Figure 3: TPR of methods using by pieces of information used 
Fig3 <- plotsim_average(res5d, met="TPR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, facetMethodType = TRUE)

Fig3
ggsave(file.path(outdir, "Figure3.pdf"), width=8, height=4)
```

@@

ggplot(rank.tab %>% filter(method != "bonf"), 
       aes(y = prop_casestudy, x = prop_yeastsim, group = prop_yeastsim, color=Method)) +
  geom_boxplot(aes(x = prop_yeastsim, y = prop_casestudy),
                   alpha = 0.3, position = position_dodge(width = 0),
                   width = 0.02) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5s)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_scaled.pdf"), width=6, height=4)

@@

uninftab <- dftab %>% 
  dplyr::filter(inform == "uninf") %>%
  dplyr::select(id, nrejects) %>%
  dplyr::rename("uninf" = "nrejects")
  #dplyr::rename(nrejects = "uninf")

@@

Fig_impactofinfcov <- ggplot(dftab, aes(x = dataset, y = method, fill = diff_inf_percent)) + 
        geom_tile() + 
        scale_fill_gradientn("% Increase\nin rejections",
                             labels = scales::percent, trans="log1p",
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.05,0,1)),
                             guide = "colorbar", limits=c(-.05,1)) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        facet_grid( ~ casestudy + cov, scales = "free", space = "free") +
        ggtitle("Impact of informative covariate on number of rejections") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.985, 0.91), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10)) +
        geom_text(aes(label = ifelse(is.na(top), "", scales::percent(top))),
                  color = "black", size = 2)

>>>>

Replaced with a pure simulation figure - see `manuscript_figures_sims.Rmd`.

@@

ggplot(rank.tab %>% filter(method != "bonf"), 
       aes(y = prop_casestudy, x = prop_yeastsim, group = prop_yeastsim, color=Method)) +
  geom_boxplot(aes(x = prop_yeastsim, y = prop_casestudy),
                   alpha = 0.3, position = position_dodge(width = 0),
                   width = 0.02) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_scaled.pdf"), width=6, height=4)

@@

uninftab <- dftab %>% 
  dplyr::filter(inform == "uninf") %>%
  dplyr::select(id, nrejects) %>%
  dplyr::rename("uninf" = "nrejects")

@@

Fig_impactofinfcov <- ggplot(dftab, aes(x = dataset, y = method, fill = diff_inf_percent)) + 
        geom_tile() + 
        scale_fill_gradientn("% Increase\nin rejections",
                             labels = scales::percent, trans="log1p",
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.05,0,1)),
                             guide = "colorbar", limits=c(-.05,1)) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        facet_grid( ~ casestudy + cov, scales = "free", space = "free") +
        ggtitle("Impact of informative covariate on number of rejections") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.985, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10)) +
        geom_text(aes(label = ifelse(is.na(top), "", scales::percent(top))),
                  color = "black", size = 2)
